Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores II. Nanoflare Trains

### 2016-08-10 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
minor corrections pointed out by PC

	\par A scaling has been claimed for hot emission with $T>T_m$ such that $\mathrm{EM}\propto T^{-b}$, with $b>0$. This fit is usually done in the range $T_m\lesssim T\lesssim10^{7.2}$. However, measured values of these ``hotward" slopes are poorly constrained due to both the low magnitude of emission and the lack of available spectroscopic data in this temperature range \citep{winebarger_defining_2012}. \citet{warren_systematic_2012} find $7\lesssim b\lesssim10$ with uncertainties of $\pm2.5-3$, for 15 AR cores though \citet{del_zanna_elemental_2014}, using observations from the Solar Maximum Mission, claim larger values for $b$. It must be noted though that reconstructing $\mathrm{EM}(T)$ from spectroscropic and narrow-band observations is non-trivial, with differrent inversion methods often giving significantly different results \citep{landi_monte_2012,guennou_can_2013,aschwanden_benchmark_2015}.

@@

	\par While a single nanoflare in the LF heating scenario will always occur in a plasma of characteristic AR density ($\sim10^9$ cm$^{-3}$) with significant consequences, nanoflare heating requires that we consider a ``train'' of nanoflares along a magnetic strand \citep{viall_patterns_2011,warren_constraints_2011,reep_diagnosing_2013,cargill_modelling_2015}. In this paper, we use an efficient two-fluid hydrodynamic model to explore the effect of a nanoflare train with varying $t_N$ on $\mathrm{EM}(T)$, in particular for $T>T_m$. Preferential species heating, NEI, power-law nanoflare distributions, and the effects of a variable $t_N$ between events are considered and an emission measure ratio metric, similar to that discussed in \citet{brosius_pervasive_2014}, is used to characterize the various results. \autoref{sec:methods} discusses the numerical model we have used to conduct this study and the parameter space we have investigated. \autoref{sec:results} shows the resulting emission measure distributions and diagnostics for the entire parameter space. In \autoref{sec:discussion}, we discuss the impacts of two-fluid effects, pre-nanoflare density, and NEI on these calculated observables and how they may be interpreted in the context of nanoflare heating. Finally, \autoref{sec:conclusions} provides some concluding comments on our findings.

@@

	where $c_2=\bar{T}_e/T_{e,a}\approx0.9$, $c_3=T_{e,0}/T_{e,a}\approx0.6$, $\nu_{ei}$ is the electron-ion binary Coulomb collision frequency, and $\psi_{TR}$ is a term included to maintain charge and current and neutrality. Additionally, $c_1=\mathcal{R}_{TR}/\mathcal{R}_C$ and its formulation is discussed in \citet{cargill_enthalpy-based_2012} with additional corrections detailed in Appendix 1 of \citetalias{barnes_inference_2016}. These equations are closed by the equations of state $p_e=k_BnT_e$ and $p_i=k_BnT_i$. In the cases where we treat the plasma as a single-fluid, we use the original EBTEL model as described in \citet{klimchuk_highly_2008,cargill_enthalpy-based_2012}.

@@

	where $t_{total}$ is the total simulation time. Note that if $H_i=H_0$ for all $i$, the heating rate for each event is $H_i=H_0=2t_{total}H_{eq}/N\tau$. Thus, for $L=40$ Mm, $A=10^{14}$ cm$^2$, the average energy per event for a loop heated by $N=20$ nanoflares in $t_{total}=8\times10^4$ s is $\varepsilon=LAt_{total}H_{eq}/N\approx5.8\times10^{24}$ erg, consistent with the energy budget of the Parker nanoflare model. 

@@

		\caption{Emission measure distributions for waiting-times $t_N=250,750,1500,2500,3750,5000$ s in the single-fluid case. The three types of heating functions shown are uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green). The solid lines in the two power-law cases show the mean $\mathrm{EM}(T)$ over $N_R$ runs and the shading indicates $1\sigma$ from the mean. The dashed lines denote the corresponding $\mathrm{EM}(T_{eff})$ distribution. The standard deviation is not included in the NEI results.}

@@

	\par From these initial results, there is an important difference in the information available in potential observations. Below $T_m$ the value of $a$ requires a specific form of the waiting time between nanoflares which in turn informs about the nature of energy release \citep{cargill_active_2014}. Above $T_m$, there is no information about the role of a waiting time, but the emission measure distribution does inform about the need for a power-law energy distribution and the density in which the nanoflare occurs. Taken together, the overall conclusion is the same: nanoflares require an \textit{intermediate frequency}. 

@@

	The relation of these results to potential solar observations is made difficult by incomplete temperature coverage. For example, we noted earlier that the temperature coverage for \textit{Hinode} and SDO is good for $T<T_m$, but patchy for $T>T_m$. On the other hand, the proposed MaGIXS instrument has the opposite performance regime. This differs from EUVE observations of some stellar coronae which have very complete temperature coverage from $10^6$ K to over $10^7$ K \citep[e.g.][]{sanz-forcada_structure_2003}, and have been modeled using low frequency nanoflares \citep{cargill_temperature-emission_2006}. In the following sub-sections we propose ways that the paucity of solar temperature coverage can be partially remedied.

@@

	\par As we discussed in the \autoref{sec:intro}, a commonly-used observable is the emission measure slope $a$ such that $\mathrm{EM}\propto T^a$ for $10^{5.5}\le T\le10^{6.6}$ K. Both observational and modeling studies have found that $2\lesssim a\lesssim5$ \citep[see Table 3 of][]{bradshaw_diagnosing_2012} and in particular, \citet{cargill_active_2014} found that a heating function of the form $t_N\propto\varepsilon$ was needed in order to account for this range of slopes. The EIS instrument \citep{culhane_euv_2007} on \textit{Hinode} permits good temperature coverage. Additionally, a similar scaling of $\mathrm{EM}\propto T^{-b}$ for $10^{6.6}\le T\le10^{7.0}$ has been claimed though measurements of $b$ have been subject to large uncertainties \citep{warren_systematic_2012} due to intermittent temperature coverage.

@@

	\section{Discussion}
	\label{sec:discussion}
	\authorcomment1{Is this section really even necessary? Can the discussion be entirely contained in (last part of) the Results section? Or we could convert \autoref{subsec:diagnostics} to the Discussion section...}

>>>>

	\par A scaling has been claimed for hot emission with $T>T_m$ such that $\mathrm{EM}\propto T^{-b}$, with $b>0$. This fit is usually done in the range $T_m\lesssim T\lesssim10^{7.2}$. However, measured values of these ``hotward" slopes are poorly constrained due to both the low magnitude of emission and the lack of available spectroscopic data in this temperature range \citep{winebarger_defining_2012}. \citet{warren_systematic_2012} find $7\lesssim b\lesssim10$ with uncertainties of $\pm2.5-3$, for 15 AR cores though \citet{del_zanna_elemental_2014}, using observations from the Solar Maximum Mission, claim larger values for $b$. It must be noted though that reconstructing $\mathrm{EM}(T)$ from spectroscropic and narrow-band observations is non-trivial, with different inversion methods often giving significantly different results \citep{landi_monte_2012,guennou_can_2013,aschwanden_benchmark_2015}.

@@

	\par Single nanoflare are a good proxy for the LF heating scenario, but a study of nanoflare heating over a range of heating frequencies requires that we consider a ``train'' of nanoflares along a magnetic strand \citep{viall_patterns_2011,warren_constraints_2011,reep_diagnosing_2013,cargill_modelling_2015}. In this paper, we use an efficient two-fluid hydrodynamic model to explore the effect of a nanoflare train with varying $t_N$ on $\mathrm{EM}(T)$, in particular for $T>T_m$. Preferential species heating, NEI, power-law nanoflare distributions, and the effects of a variable $t_N$ between events are considered and an emission measure ratio metric, similar to that discussed in \citet{brosius_pervasive_2014}, is used to characterize the various results. \autoref{sec:methods} discusses the numerical model we have used to conduct this study and the parameter space we have investigated. \autoref{sec:results} shows the resulting emission measure distributions and diagnostics for the entire parameter space. In \autoref{sec:discussion}, we discuss the impacts of two-fluid effects, pre-nanoflare density, and NEI on these calculated observables and how they may be interpreted in the context of nanoflare heating. Finally, \autoref{sec:conclusions} provides some concluding comments on our findings.

@@

	where $c_2=\bar{T}_e/T_{e,a}\approx0.9$, $c_3=T_{e,0}/T_{e,a}\approx0.6$, $\nu_{ei}$ is the electron-ion binary Coulomb collision frequency, and $\psi_{TR}$ is a term included to maintain charge and current and neutrality. Additionally, $c_1=\mathcal{R}_{TR}/\mathcal{R}_C$ and its formulation is discussed in \citet{cargill_enthalpy-based_2012} with additional modifications detailed in Appendix 1 of \citetalias{barnes_inference_2016}. These equations are closed by the equations of state $p_e=k_BnT_e$ and $p_i=k_BnT_i$. In the cases where we treat the plasma as a single-fluid, we use the original EBTEL model as described in \citet{klimchuk_highly_2008,cargill_enthalpy-based_2012}.

@@

	where $t_{total}$ is the total simulation time. Note that if $H_i=H_0$ for all $i$, the heating rate for each event is $H_i=H_0=2t_{total}H_{eq}/N\tau$. Thus, for $L=40$ Mm, $A=10^{14}$ cm$^2$, the average energy per event for a loop heated by $N=20$ nanoflares in $t_{total}=8\times10^4$ s is $\varepsilon=LAt_{total}H_{eq}/N\approx5.8\times10^{24}$ erg. 

@@

		\caption{Emission measure distributions for waiting-times $t_N=250,750,1500,2500,3750,5000$ s in the single-fluid case. The three types of heating functions shown are uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green). Note that in some panels, the blue $\beta=0$ curves may not be visible because they overlap heavily with the green $\beta=1$ curves. The solid lines in the two power-law cases show the mean $\mathrm{EM}(T)$ over $N_R$ runs and the shading indicates $1\sigma$ from the mean. The dashed lines denote the corresponding $\mathrm{EM}(T_{eff})$ distribution. The standard deviation is not included in the NEI results.}

@@

	\par From these initial results, there is an important difference in the information available in potential observations. Below $T_m$ the observed values of $a$ require a specific form of the waiting time between nanoflares which in turn informs about the nature of energy release \citep{cargill_active_2014}. Above $T_m$, there is no information about the role of a waiting time, but the emission measure distribution does inform about the need for a power-law energy distribution and the density in which the nanoflare occurs. Taken together, the overall conclusion is the same: nanoflares require an \textit{intermediate frequency}. 

@@

	The relation of these results to potential solar observations is made difficult by incomplete temperature coverage. For example, we noted earlier that the temperature coverage for \textit{Hinode} and SDO is good for $T<T_m$, but patchy for $T>T_m$. On the other hand, the proposed MaGIXS \citep{kobayashi_marshall_2011,winebarger_new_2014} instrument has the opposite performance regime. This differs from EUVE observations of some stellar coronae which have very complete temperature coverage from $10^6$ K to over $10^7$ K \citep[e.g.][]{sanz-forcada_structure_2003}, and have been modeled using low frequency nanoflares \citep{cargill_temperature-emission_2006}. In the following sub-sections we propose ways that the paucity of solar temperature coverage can be partially remedied.

@@

	\par As we discussed in the \autoref{sec:intro}, a commonly-used observable is the emission measure slope $a$ such that $\mathrm{EM}\propto T^a$ for $10^{5.5}\le T\le10^{6.6}$ K. Both observational and modeling studies have found that $2\lesssim a\lesssim5$ \citep[see Table 3 of][]{bradshaw_diagnosing_2012} and in particular, \citet{cargill_active_2014} found that a heating function of the form $t_N\propto\varepsilon$ was needed in order to account for this range of slopes. In this range, the EIS instrument \citep{culhane_euv_2007} on \textit{Hinode} permits good temperature coverage. Additionally, a similar scaling of $\mathrm{EM}\propto T^{-b}$ for $10^{6.6}\le T\le10^{7.0}$ has been claimed though measurements of $b$ have been subject to large uncertainties \citep{warren_systematic_2012} due to intermittent temperature coverage.

@@
